### 2017-10-15 Draft2.tex
Apex of madness

	$$
	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
	$$

@@

	so the goal is now to find a formula for $\nwritesresizefn(i)$. First note that all of the writing in [resize] comes from the call to [add] on a dynamic array. Let the initial capacity of the dynamic array be $\initcapacity$ and its growth factor be $\growthfactor$. We showed before that

>>>>

	[ref1]
	$$
	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
	$$

@@

	so the goal is now to find a formula for $\nwritesresizefn(i)$. First note that all of the writing in [resize] comes from the call to [add] on a dynamic array. Let the initial capacity of the dynamic array be $\initcapacity$, its growth factor be $\growthfactor$, and its write cost function be $\nwritesfn(k)$. In [ref1] we derived a formula for $\nwritesfn(k)$,
